\documentclass[english,BCOR=1.5cm,twoside]{tudscrreprt}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{isodate}
\usepackage{listings}

\usepackage[
    style=numeric-comp,
    backend=biber,
    url=false,
    doi=false,
    isbn=false,
    hyperref,
]{biblatex}
\addbibresource{bibliography.bib}
\AtEveryBibitem{
    \clearfield{note}
}

\usepackage[hidelinks]{hyperref}
\usepackage[capitalise,nameinlink,noabbrev]{cleveref}

% \usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}

\usepackage{graphicx}
\graphicspath{ {../images/} }

% if you need mathy stuff
\newtheorem{lem}{Lemma}
\crefname{lem}{Lemma}{Lemmas}
\newtheorem{thm}{Theorem}
\crefname{thm}{Theorem}{Theorems}
\newtheorem{defs}{Definition}
\crefname{defs}{Def.}{Defs.}

\usepackage{blindtext}

\usepackage{csquotes}

\usepackage{caption}
\captionsetup{font=sf,labelfont=bf,labelsep=space}
\usepackage{floatrow}
\floatsetup{font=sf}
\floatsetup[table]{style=plaintop}
\captionsetup{singlelinecheck=off,format=hang,justification=raggedright}
\DeclareCaptionSubType[alph]{figure}
\DeclareCaptionSubType[alph]{table}
\captionsetup[subfloat]{labelformat=brace,list=off}

\usepackage{booktabs}
\usepackage{array}
\usepackage{tabularx}
\usepackage{tabulary}
\usepackage{tabu}
\usepackage{longtable}
\usepackage{quoting}
\usepackage[babel]{microtype}
\usepackage{xfrac}
\usepackage{scrhack}

\usepackage{enumitem}
\setlist[itemize]{noitemsep}

\usepackage{ellipsis}
\let\ellipsispunctuation\relax

\input{lst.tex}

\begin{document}

% METADATA SECTION
% °°°°°°°°°°°°°°°°

\faculty{Fakultät Informatik}
\department{}
\institute{Institut für Software- und Multimediatechnik}
\chair{Lehrstuhl für Softwaretechnologie}
\title{Quality Testing Concepts} % TODO: Update. Some Error occurs ...
\thesis{bachelor}
\graduation[B.Sc.]{Bachelor of Science}
\author{Paul Erlenwein}
\emailaddress[]{paul.erlenwein@tu-dresden.de}
\matriculationnumber{4609464}
\matriculationyear{2016}
\dateofbirth{31.12.1996}
\placeofbirth{Ludwigshafen}
\course{Distributed Systems Engineering}
\supervisor{
    Dr.-Ing. Birgit Demuth
    \and Markus Hamann
    \and Dr. Sebastian Götz % ??
}
\professor{Prof. Dr. rer. nat habil. Uwe Aßmann}
\date{05.02.2021}
\maketitle
\newpage

\tableofcontents
\listoffigures
\listoftables

% IMPORT SECTION
% °°°°°°°°°°°°°°

\input{sections/introduction}
\input{sections/related_work}
\input{sections/design}
\input{sections/realization}

\printbibliography[heading=bibintoc]\label{sec:bibliography}

\appendix
\input{sections/appendix}

\confirmation

\end{document}